---
title: "WOSdocumentation"
author: "wkumler"
date: "April 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(wosr)
```

##To be interlaced elsewhere:
TS= Topic 
TI= Title 
AU= Author
AI= Author Identifiers 
GP= Group Author [Index] 
ED= Editor 
SO= Publication Name [Index] 
DO= DOI 
PY= Year Published 
CF= Conference 
AD= Address 
OG= Organization-Enhanced [Index] 
OO= Organization 
SG= Suborganization
SA= Street Address 
CI= City 
PS= Province/State 
CU= Country/Region 
ZP= Zip/Postal Code 
FO= Funding Agency 
FG= Grant Number 
FT= Funding Text 
SU= Research Area 
WC= Web of Science Category 
IS= ISSN/ISBN 
UT= Accession Number 
PMID= PubMed ID 
ALL= All Fields 

## WOS tool

As stated in the README, I'd like to be able to access the Web Of Science tools to do some data analysis myself.

Part of the trick here is getting an authentication without an authentication - fortunately, the WOS tools that came with the wos Python package allow us to request "lite" access, which produces an SID that we'll try to steal. This is accessed via the system command "wos" and various flags.

To save the bash output as an accessible variable, we use the syntax from [Stack Overflow](https://stackoverflow.com/questions/4651437/how-do-i-set-a-variable-to-the-output-of-a-command-in-bash)

> In addition to backticks (\`command\`), you can use $(command), which I find easier to read, and allows for nesting.

> OUTPUT="$(ls -1)"
> echo "${OUTPUT}"

### Attempt \#1

```{bash auth}
#SID="$(wos --lite query 'AU=Wickham Hadley')"
#echo $SID
```

The code throws an error, but we've got the SID we needed!

```{r access, error=T}
print(SID)
```

I was really hoping that I'd be able to access the SID variable automatically in
the following R block, but no luck.

### Attempt \#2

If we can't access SID natively, perhaps we can export it as an environmental
variable and access it otherwise?

```{bash auth2}
#export SID="$(wos --lite query 'AU=Wickham Hadley')"
```

```{r access2, error=T}
Sys.getenv(SID)
```

No dice. Damn.

### Attempt \#3: yes!

Okay, rather than fiddling with bash and python and other languages, let's just
make a system call within R. Only works in Ubuntu?

```{r SID}
#v <- system("wos --lite query 'AU=Wickham Hadley'") # Doesn't work: returns v empty

v <- system("wos --lite query 'AU=Wickham Hadley'", intern = T) #Works!

SID <- v[1]
SID <- gsub('Authenticated \\(SID: ', "", SID)
SID <- gsub(")", "", SID)

print(SID)
```

Yay! So we've got an SID that we can use to access WOS lite.

```{r WOS, error=T}
library(wosr)

pull_wos("AU=Wickham Hadley", sid = SID) # Throws an error - not authorized

pull_wos("AU=Wickham Hadley", sid = SID, editions = "CCR") # Throws an error - not authorized

query_wos("AU=Wickham Hadley", sid = SID) # Throws an error - not authorized
```

Damn. Looks like wosr is only set up to query paid data sets. Time to do it the long way!

We can construct our GET and POST requests manually. By looking into the wosr 
query_wos data, we can see how they're doing it:

> response <- httr::POST("http://search.webofknowledge.com/esti/wokmws/ws/WokSearch", 
        body = body, httr::add_headers(cookie = sprintf("SID=%s", 
            sid)), ua(), ...)
            
> body <- paste0("<soapenv:Envelope xmlns:soapenv=\"http://schemas.xmlsoap.org/soap/envelope/\"\n    xmlns:woksearch=\"http://woksearch.v3.wokmws.thomsonreuters.com\">\n    <soapenv:Header/>\n    <soapenv:Body>\n    <woksearch:search>\n    <queryParameters>\n    <databaseId>WOS</databaseId>\n    <userQuery> ", 
        escape_query(query), 
        " </userQuery>", 
        paste_eds(editions), 
        "<queryLanguage>en</queryLanguage>\n    </queryParameters>\n    <retrieveParameters>\n    <firstRecord>1</firstRecord>\n    <count>0</count>\n    </retrieveParameters>\n    </woksearch:search>\n    </soapenv:Body>\n    </soapenv:Envelope>")
            
Let's try that with the different endpoint "http://search.webofknowledge.com/esti/wokmws/ws/WokSearchLite",
found [here](http://help.incites.clarivate.com/wosWebServicesLite/WebServicesLiteOverviewGroup/Introduction/serviceEndpointAddresses.html)

```{r POST}
library(httr)
library(XML)
library(xml2)

endpoint = "http://search.webofknowledge.com/esti/wokmws/ws/WokSearchLite"

query <- "AU=Knuth Donald" #This may break when passing an ampersand: see wosr:::escape_query

bod1 <- "<soapenv:Envelope xmlns:soapenv=\"http://schemas.xmlsoap.org/soap/envelope/\"\n    xmlns:woksearch=\"http://woksearch.v3.wokmws.thomsonreuters.com\">\n    <soapenv:Header/>\n    <soapenv:Body>\n    <woksearch:search>\n    <queryParameters>\n    <databaseId>WOS</databaseId>\n    <userQuery> "
bod2 <- " </userQuery>"
bod3 <- "<queryLanguage>en</queryLanguage>\n    </queryParameters>\n    <retrieveParameters>\n    <firstRecord>1</firstRecord>\n    <count>0</count>\n    </retrieveParameters>\n    </woksearch:search>\n    </soapenv:Body>\n    </soapenv:Envelope>"

body <- paste0(bod1, query, bod2, SID, bod3)

response <- POST(endpoint, body = body, add_headers(cookie = paste0("SID=", SID)), wosr:::ua())


raw_xml <- httr::content(response, as = "text")
unescaped_xml <- wosr:::unescape_xml(raw_xml)
unescaped_xml <- paste0("<x>", unescaped_xml, "</x>")
doc <- read_html(unescaped_xml)


query_id <- wosr:::parse_el_txt(doc, xpath = "//queryid")
rec_cnt <- wosr:::parse_el_txt(doc, xpath = "//recordsfound")
structure(list(query_id = as.numeric(query_id), rec_cnt = as.numeric(rec_cnt), 
               sid = SID), class = "query_result")
```

So that didn't work, and is instead returning an Error 500 - server weirdness.

Possible problems:

1. The server knows that the SID is coming from different places

2. The request is poorly-formed

3. The server isn't handling things correctly

Breaking things down a little, let's try fixing the first problem. We're going
to use httr to obtain an SID instead of the system workaround above. This is
also good practive with POST and checks that we've got some things figured out.

```{r APIhalp}
endpoint = "http://search.webofknowledge.com/esti/wokmws/ws/WokSearchLite"

query <- "AU=Knuth Donald" #This may break when passing an ampersand: see wosr:::escape_query

bod1 <- "<soapenv:Envelope xmlns:soapenv=\"http://schemas.xmlsoap.org/soap/envelope/\"\n xmlns:woksearchlite=\"http://woksearchlite.v3.wokmws.thomsonreuters.com\"> <soapenv:Header/>    <soap:Body>\n    <woksearchlite:search>\n    <queryParameters>\n    <databaseId>WOS</databaseId>\n    <userQuery> "
bod2 <- " </userQuery>     <editions>\n     <collection>WOS</collection>/n     <edition>SCI</edition>\n    </editions>\n    <timeSpan>\n    <begin>2000-01-01</begin>\n    </end>2011-12-31</end>\n    </timespan>\n    <queryLanguage>en</queryLanguage>\n    </queryParameters>\n    <retrieveParameters>\n    <firstRecord>1</firstRecord>\n    <count>5</count>\n    </retrieveParameters>\n    </woksearchlite:search>\n    </soapenv:Body>\n    </soapenv:Envelope>"

body <- paste0(bod1, query, bod2)

response <- POST(endpoint, body = body, add_headers(cookie = paste0("SID=", SID)))
```

Still no luck, having updated all the URL pieces to the proper spots. Let's push ahead with the proper authorize procedure.

```{r APIauth}
endpoint <- "http://search.webofknowledge.com/esti/wokmws/ws/WOKMWSAuthenticate"

body <- '<soapenv:Envelope xmlns:soapenv="http://schemas.xmlsoap.org/soap/envelope/"\n    xmlns:auth="http://auth.cxf.wokmws.thomsonreuters.com">\n    <soapenv:Header/>\n    <soapenv:Body>\n        <auth:authenticate/>\n    </soapenv:Body>\n    </soapenv:Envelope>'

response <- POST(endpoint, body = body)

raw_SID = response$headers$`set-cookie`
SID = gsub("SID=", "", raw_SID)
```

So that worked - status code 200, SID returned as a cookie header. Cool!

The next step appears to be to run a search for a query, followed by a request for the searched resource.

```{r APIsearch}
endpoint <- "http://search.webofknowledge.com/esti/wokmws/ws/WokSearchLite"

query <- "AU=Koehl Mimi"
#query <- "TS=(cadmium OR lead)"

bod1 <- '<soapenv:Envelope xmlns:soapenv="http://schemas.xmlsoap.org/soap/envelope/"\n    xmlns:woksearchlite="http://woksearchlite.v3.wokmws.thomsonreuters.com">\n    <soapenv:Header/>\n    <soapenv:Body>\n    <woksearchlite:search>\n    <queryParameters>\n    <databaseId>WOS</databaseId>\n    <userQuery>'

#bod2 <- '</userQuery>\n    <editions>\n    <collection>WOS</collection>\n    <edition>SCI</edition>\n    </editions>\n    <timeSpan>\n    <begin>2000-01-01</begin>\n    <end>2011-12-31</end>\n    </timeSpan>\n    <queryLanguage>en</queryLanguage>\n    </queryParameters>\n    <retrieveParameters>\n    <firstRecord>1</firstRecord>\n    <count>5</count>\n    </retrieveParameters>\n    </woksearchlite:search>\n    </soapenv:Body>\n    </soapenv:Envelope>'

bod2 <- '</userQuery>\n    <timeSpan>\n    <begin>1900-01-01</begin>\n    <end>2050-12-31</end>\n    </timeSpan>\n    <queryLanguage>en</queryLanguage>\n    </queryParameters>\n    <retrieveParameters>\n    <firstRecord>1</firstRecord>\n    <count>5</count>\n    </retrieveParameters>\n    </woksearchlite:search>\n    </soapenv:Body>\n    </soapenv:Envelope>'

body <- paste0(bod1, query, bod2)

response <- POST(endpoint, body = body, add_headers(cookie=paste0("SID=", SID)))

doc <- wosr:::get_xml(response)
query_id <- wosr:::parse_el_txt(doc, xpath = "//queryid")
rec_cnt <- wosr:::parse_el_txt(doc, xpath = "//recordsfound")
structure(list(query_id = as.numeric(query_id), rec_cnt = as.numeric(rec_cnt), 
               sid = SID), class = "query_result")
```

Also working! Awesome. Curiously, querying AU seems to be different from querying topics:

  - AU=Knuth Donald: 1 matching record
  - AU=Koehl Mimi: 0 matching records
  - AU=Smith John: 249 matching records
  
Are those the number of unique authors with that name? And therefore Mimi doesn't show up at all?

UPDATE: Modifying the parameters passed to the request recovers all 12 of Mimi's
papers that show up when interacting with the WOS GUI. Yay! I removed the time
range and the editions tags.



